Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-29 paper_jasa.tex
p-value vs prop-correct figure added

\green{Add figure showing proportion correct vs p-value of actual data plot for experiments 1 and 2.}

@@

\green{Where is Figure \ref{fig:pval_definition} referred to and discussed?}

@@

%\begin{figure*}[hbtp]
%   \centering
%       \scalebox{0.6}{\includegraphics{p_val_percent_correct.pdf}}
%       \caption{Percentage of correct responses decreases rapidly with the increase of p-value. After p-value exceeds 0.15 it is very unlikely to identify the actual plot. The theoretical justification of this is shown in figure \ref{fig:pval_power}. \blue{The scenario is different for experiment 3. $p$-value does not seem to have any effect on percent correct. This may be due to Type-III error.} \green{p-value on log scale?} }
%       \label{fig:pval_pcorrect}
%\end{figure*}

>>>>

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_percent_correct.pdf}}
       \caption{Proportion of correct responses decreases rapidly with the increase of p-value. After p-value exceeds 0.15 it is very unlikely to identify the actual plot. The theoretical justification of this is shown in figure \ref{fig:pval_power}. }
       \label{fig:pval_pcorrect}
\end{figure*}

%\green{Add figure showing proportion correct vs p-value of actual data plot for experiments 1 and 2.}

@@

\green{Where is Figure \ref{fig:pval_definition} referred to and discussed?} \blue{Are we going to keep both figures \ref{fig:pval_definition} and \ref{fig:pval_plot_signal}?}

@@
